---
title: "The central limit theorem"
author: "Hadley Wickham"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
# include = FALSE suppresses the output of this block
library(rv2)
```

This vignette shows how we can see the central limit theorem emerge when we sum multiple discrete random variables together.

We'll start by creating a helper function that adds together a random variable `n` times,  then divides by `n`

```{r}
mean_n <- function(x, n) {
  out <- x
  for (i in seq_len(n - 1)) {
    out <- out + x
  }
  out / n
}
```

Let look what happens to the average from rolling a die:

```{r}
dice <- rv(1:6)
plot(dice)
plot(mean_n(dice, 2))
plot(mean_n(dice, 3))
plot(mean_n(dice, 10))
```

Even if we have a highly non-normal distribution to start with, it still converges eventually:

```{r}
skewed <- rv(c(1, 10), c(0.9, 0.1))
plot(skewed)
plot(mean_n(skewed, 10))
plot(mean_n(skewed, 50))
plot(mean_n(skewed, 100))
```
